%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Preamble
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%% The uwthesis.sty file relies on the memoir class!
%%%% You should be using the memoir class anyway; it makes life easier:
%%%% http://www.ctan.org/tex-archive/macros/latex/contrib/memoir/
\documentclass[oneside, letterpaper, 12pt, oldfontcommands]{memoir}
%%%% Import uwthesis.sty to get official formatting, then set your variables.
\usepackage{uwthesis}
\usepackage{cite}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{rotating} % for sidewaystable
\usepackage{feynmp}
\usepackage{xspace}
\usepackage{amsmath}
\usepackage{helpers}
\usepackage{hyperref}
\usepackage[labelfont={bf,it},font={it}]{caption}
\DeclareGraphicsRule{.1}{mps}{*}{} %feynmp crap has .1 extension for some reason
\DeclareGraphicsExtensions{%
    .pdf,.PDF,% use PDFs first!
    .png,.PNG,%
    .jpg,.mps,.jpeg,.jbig2,.jb2,.JPG,.JPEG,.JBIG2,.JB2}

\graphicspath{ {figs/} {figs/BGs/} {figs/unfolded/} {figs/results/} }

\settitle{Discovery of the Higgs Boson and a Search for Beyond the Standard Model Physics in ZZ
Decays using the CMS Detector at the LHC}
\setauthor{Ian Ross}
\setdepartment{Physics}
\doctors % or \masters
\setgraddate{2013}
\setdefensedate{8.August.2013} % or whatever format you want

%%%% Members of the Final Oral Committee (FOC)
%%%% Give name, rank, and department
%%%% 
\setfoca{Sridhara Dasu}{Professor}{Physics} % <- Your advisor
\setfocb{Wesley Smith}{Bjorn Wiik Professor}{Physics}
\setfocc{Matt Herndon}{Professor}{Physics}
\setfocd{Vernon Barger}{Vilas Professor}{Physics}
\setfoce{Terry Millar}{Professor}{Mathematics}

%%%% Your abstract, used for the UMI abstract and in your front matter
\setabstract{%

A study of the $pp \rightarrow ZZ \rightarrow \ell\ell\ell\ell$ final state is
conducted using 19.6~\fbinv of 8 TeV proton-proton collisions at the LHC using the CMS
detector. The Standard Model $pp \rightarrow ZZ$ production cross section is
measured to be 
%$\sigma(pp\rightarrow ZZ) = 
$7.7^{+0.5}_{-0.5} \textrm(stat.) ^{+0.6}_{-0.5}
\textrm{(sys.)}  \pm 0.3 \textrm{(lumi)}~\textrm{pb} $. Evidence of a new
Higgs-like boson is observed with a significance of $6.1 \sigma$ at 126~GeV.
95\% confidence level upper limits are set on the neutral anomalous triple gauge
couplings; $-0.004 < f_4^Z < 0.004$, $-0.005 < f_4^{\gamma} < 0.005$, $-0.004 <
f_5^Z < 0.004$, and $-0.005 < f_5^{\gamma} < 0.005$.

}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Document
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% Tell the memoir class to set up lowercase roman for pagination, etc.
\frontmatter

%%%% Uncomment this to create a UMI abstract page.
%%%% If you are submitting electronically, however, this page is unnecessary.
% \theumiabstract

% The title page
\thetitlepage
\clearpage

% The copyright page, if you want to pay the fee and register copyright.
%\thecopyrightpage
%\cleardoublepage

% These above pages should not be counted, so we reset the counter to 1.
\setcounter{page}{1}

% An abstract may be required by your department.
\section{Abstract}
\uwabstract
\cleardoublepage

% Acknowledgements go here if you want to include them.
\section{Acknowledgements}
Acknowledgement is owed to many, and I deeply apologize for those who I've
left off this list (it's not intentional, I promise). Many thanks:

To Sridhara Dasu, Wesley Smith, and Matt Herndon for their endless support,
knowledge, and bountiful advice.

To Sascha Savin, for his patience, help, and ideas.

To Evan Friis and Maria Cepeda, for their wisdom and friendship.

To my fellow UW CMS students, past and present, for the support (be it
programming, physics, RCT, or life-related), and all the good times. Marc
Weinberg, Kira Grogg, Michalis Bachtis, Christos Lazaridis, Mike Anderson, Jeff
Klukas, Lindsey Gray, Jessica Leonard, Joshua Swanson, Isobel Ojalvo, Austin
Belknap, and all the rest -- I owe pieces of this work to each of you.

To my friends, in Madison and beyond, for always being there for me, even when
I was an ocean away.

To the HZZ4L Group, whose collective efforts are reflected in my work.

And to my family: my sister, Cameron, and my parents, Doug and Judy, for their
support and love. I couldn't have done it without you.


\clearpage

% Table of contents
\maxtocdepth{subsection}
\tableofcontents* % the * means that there isn't an entry for the TOC itself
\clearpage
\listoffigures  % if you have any figures
\clearpage
\listoftables   % if you have any tables

% Tell the memoir class to set up normal pagination, etc. for the main doc
\mainmatter

\setcounter{secnumdepth}{2} %allow subsubsection references

\input{Introduction}
\input{sm}
\input{previous}
\input{expOverview}
\input{eventGenSim}
\input{eventReco}
\input{analysis}
\input{results}
\input{conclusions}


\bibliography{bibliography}{}
\bibliographystyle{unsrt}

\end{document}
